Usage metrics

### 2020-12-09 inst/analysis/usage_metrics.Rmd
Dataset .10

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.9/summarized-packages.fst
  corpus_path: /revalstudy/inst/data/corpus.fst
---

@@

```{r file-info, echo=FALSE}
file_info(params$calls_packages_path)
```

```{r read-data}
eval_calls <- read_fst(paste0(params$base_dir, params$calls_packages_path)) %>% as_tibble()
```

@@

```{r eval-calls-overview}
# own_eval_calls <- eval_calls %>% filter(eval_source == package) # probably to remove
own_eval_calls <- eval_calls
nb_eval_calls <- (own_eval_calls %>% count(wt = nb_ev_calls))$n

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.10/summarized-packages.fst
  corpus_path: /run/package-evals-traced.10/corpus.fst
---

@@

```{r file-info, echo=FALSE}

calls_packages_path <- paste0(params$base_dir, params$calls_packages_path)
file_info(calls_packages_path)

eval_calls <- read_fst(calls_packages_path) %>% as_tibble()
```

@@

```{r eval-calls-overview}
own_eval_calls <- eval_calls
nb_eval_calls <- (own_eval_calls %>% count(wt = nb_ev_calls))$n
